\documentclass[color=NavyBlue]{devResume}

\begin{document}
    \name{Lukas Einler Larsson}
    \info{
        \birthday{17\textsuperscript{st} Aug 1999}
        \phone{+46 73 685 56 38}
        \location{Gothenburg, Sweden}

        \email{lukas0817@gmail.com}
        \linkedin{lukas-einler-larsson}
        \github{Itggot-lukas-einlerlarsson}
        \publication{resolve?urn=urn:nbn:se:bth-24984}
    }

    \cvContent{
        \cvHeader
        \cvSection{Profile}
            I am a curious and ambitious problem solver based in Gothenburg, Sweden. I studied IT-security and software development at Bleking Tekniska Högskola in Karlskrona, Blekinge. Me and my classmate's bachelor thesis has been submitted to the journal "Journal of Information Security and Applications"; Elsevier publishing, soon to be published.

        \cvSection{Employment}
            \cvPosition{Developer / DevSecOps Engineer}{SAAB}{Gothenburg, Sweden}{Aug 2023 - Ongoing}
                {
                    \item[--] Worked in an IT compartment called Software Factory, mainly working with developing and setting up CI/CD pipelines and servers.
                    \item[--] This job gave me lots of knowledge about linux, bash scripting and linux software.
                    \item[--] Designed (with Plant UML) and developed a program in python that continiously searched for updates and transferred updated git and artifactory data to different security environments within SAAB.
                    \item[--] Worked with small webservers (python-flask) to setup api's between systems and I have created e.g. a Mattermost bot. I have also worked with SSL certificates and reverse proxies such as NGINX.
                    \item[--] Used docker/podman and docker compose to setup local servers. I have also setup servers in k8s.
                    \item[--] Built containers for generic purposes and also more specific containers with python programs in them.
                    \item[--] Setting up Jenkins pipelines that fetches data, tests data, run static code testing (sonarqube) and then builds a container/binary.
                    \item[--] I have worked with Scrum and with Kanban.
                    \item[--] Continiously supported the software that I have helped develop and setup.
                    \item[--] Worked with export controlled and nationally classified information. 
                }


            \cvPosition{IT-support}{Telia}{Gothenburg, Sweden}{Dec 2019 - June 2020}
                {
                    \item[--] I worked in the Technical Support department with customers over the phone, mainly helping customers with problems surrounding their fiber broadband connection and mobile phone services.
                    \item[--] This job gave me knowledge about how to professionally work with customers and colleagues over digital communication.
                    \item[--] The job also knowledge about customer service and working with support systems.
                }

        \cvSection{Background}
            Beyond working and being intrested in IT and software development I have worked many jobs during my semesters.
            I have worked with renting out and setting up tents many summers (Kikiriki AB), This was a job where I had to meet new customers all the time and drove around Gothenburg in a boxtruck.
            I have worked with customer service at Biltema AB in Hisingsbacka in Gothenburg.
            I have worked as a referee in floorball.

            \smallskip
            I have also studied Jazz at Geijer Skolan in Ransäter, Sweden. I mainly studied jazz guitar and played with a small acoustic ensamble and in a big band where i played lead electric guitar. Today I play lead guitar in a cover band.

    }
    \cvSidebar{
        \cvSection{\emphasis{personality} traits}
            \cvTag{Curious}{100}
            \cvTag{Responsible}{100}
            \cvTag{Patient}{80}
            \cvTag{Analytical}{80}
            \cvTag{Persistent}{70}
            \cvTag{Loyal}{70}
            \cvTag{Direct}{80}

        \cvSection{\emphasis{cognitive} skills}
            \progressArc{80\%}{Adaptability}{80}
            \progressArc{70\%}{Work under pressure}{70}
            \newline
            \progressArc{75\%}{Multitasking}{65}
            \progressArc{90\%}{Logic and reasoning}{90}

        \cvSection{\emphasis{strengths}}
            \cvSkill{Software development}{5}
            \cvSkill{Linux and bash scripting}{4}
            \cvSkill{Docker compose}{4}
            \cvSkill{Docker/podman}{4}
            \cvSkill{Leadership}{3}
            \cvSkill{kubernetes}{2}

        \cvSection{key \emphasis{technical} skills}
            \cvTag{python}{100}
            \cvTag{bash}{80}
            \cvTag{unittesting}{80}
            \cvTag{integrationtesting}{70}
            \cvTag{sonarqube}{70}
            \cvTag{jira}{60}
            \cvTag{jenkins}{60}
            \cvTag{sonarqube}{60}
            \cvTag{flask}{70}
            \cvTag{django}{40}
            \cvTag{HTML5}{30}
            \cvTag{git}{70}
            \cvTag{c++}{30}
            \cvTag{rust}{25}
            \cvTag{react}{25}
            \cvTag{PlantUML}{70}
            \cvTag{Object-oriented design}{60}
            \cvTag{Groovy}{60}
            \cvTag{LDAP}{60}

        \cvSection{my \emphasis{education}}
            \cvEducation{BS.c. studies}
            {IT - Security}
            {2020 - 2023, Blekinge Tekniska Högskola}
            \bigskip
            \cvEducation{High School studies
            \hspace{1em}\faGraduationCap\hspace{0.25em}\color{body} 2018}
            {IT}
            {2015 - 2018, IT-Gymnasiet Göteborg}

        \cvSection{\emphasis{languages} i speak}
            \cvSkill{Swedish}{5}
            \cvSkill{English}{5}
            \cvSkill{German}{1}

        \cvSection{what i \emphasis{enjoy}}
            \cvHobby{Travel}{\faGlobeEurope}
            \cvHobby{Guitar}{\faGuitar}
            \cvHobby{Disc golf}{\faCookie}

        \cvSection{References}
            Upon request
    }
\end{document}